When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-06-14 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added figure with motivation (moved fr supplement)

When asking participants what motivated their decisions in the cognitive effort discounting paradigm, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
Figure S.1 in the Supplementary Material shows the different motivations in the context of the SVs per $n$-back level.

@@

>>>>

When asking participants what motivated their decisions in the cognitive effort discounting paradigm, `r format(round((table(data_quest$motivation)[1]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid boredom, `r format(round((table(data_quest$motivation)[2]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted a challenge, `r format(round((table(data_quest$motivation)[3]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to avoid effort, and `r format(round((table(data_quest$motivation)[4]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% stated that they wanted to relax.
The remaining `r format(round((table(data_quest$motivation)[5]/sum(table(data_quest$motivation)))*100, digits = 1), nsmall = 1)`% of participants used the free text field and provided reasons such as "I wanted a fair relation of effort and reward.", "I wanted the fun that I had in the more challenging levels.", "I wanted to maximize reward first and minimize effort second.", or "I did not want to perform poorly when I was being paid for it.".
Figure \@ref(fig:motivation) shows the different motivations in the context of the SVs per $n$-back level.

[FIGURE \@ref(fig:motivation) HERE]

@@

```{r motivation, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective values per $n$-back level for each participant, grouped by the motivation for effort discounting that they indicated in the single choice question after the paradigm. $N=116$. 'Other' opened up a free text field, in which participants gave responses such as 'I wanted fair pay for my effort', 'I wanted to have fun', and 'I wanted to maximize the reward'. Figure available at osf.io/vnj8x/, under a CC-BY-4.0 license.", fig.pos="H"}

  include_graphics(here("06_Paper", "COG-ED", "Stage 2", "Figures", "motivation.png"))
